The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
update years
todo check res, mention raster package?

### Caribou location data
We used GPS location data collected from Fogo Island caribou in 2018. Adult
female caribou were immobilized and fitted with global positioning system (GPS)
collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars, 1,250 g)
as described by Schaefer and Mahoney (2013). Collars were programmed to collect
location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
discrete removed all erroneous and outlier GPS fixes following Bjørneraas et al.
(2010). We did not collar all female caribou in the herd; however, we assumed
that our sample of collared animals was random.

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador
Wildlife Division. Available landcover classification included nine habitat
types at 30 x 30m resolution. We distilled the landcover types into three broad
categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
consisted of lichen habitat, open habitat consisted of wetland, rocky barrens,
and anthropogenic habitat types, while forest habitat consisted of coniferous
forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
Water habitat was excluded from all subsequent analyses.

>>>>

### Caribou location data
We used GPS location data collected from Fogo Island caribou in 2017 and 2018. Adult
female caribou were immobilized and fitted with global positioning system (GPS)
collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars, 1,250 g)
as described by Schaefer and Mahoney (2013). Collars were programmed to collect
location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
discrete removed all erroneous and outlier GPS fixes following Bjørneraas et al.
(2010). We did not collar all female caribou in the herd; however, we assumed
that our sample of collared animals was random.

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador
Wildlife Division. Available landcover classification included nine habitat
types at <!-- TODO: double check --> 30m resolution. We reclassified the landcover types into three
categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
consisted of lichen habitat, open habitat consisted of wetland, rocky barrens,
and anthropogenic habitat types, while forest habitat consisted of coniferous
forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
Water habitat was excluded from all subsequent analyses. 
<!-- using the raster package for R? -->
